---
output: rmarkdown::github_document
---

[Travis-CI Build Status](https://travis-ci.org/hrbrmstr/rep.svg?branch=master) | 
[AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/hrbrmstr/rep?branch=master&svg=true) | 
[Coverage Status](https://img.shields.io/codecov/c/github/hrbrmstr/rep/master.svg)

# rep

Tools to Parse and Test Robots Exclusion Protocol Files and Rules

## Description

The 'Robots Exclusion Protocol' <http://www.robotstxt.org/orig.html> documents a set of standards for allowing or excluding robot/spider crawling of different areas of site content. Tools are provided which wrap The 'rep-cpp` <https://github.com/seomoz/rep-cpp> C++ library for processing these 'robots.txt' files.

- [`rep-cpp`](https://github.com/seomoz/rep-cpp)
- [`url-cpp`](https://github.com/seomoz/url-cpp)

## Tools

The following functions are implemented:

- `can_fetch`:	Test URL path against robots.txt
- `crawl_delays`:	Get all agent crawl delay values
- `print.robxp`:	Custom printer for 'robexp' objects
- `robxp`:	Create a robots.txt object

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/rep")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(rep)
library(robotstxt)

# current verison
packageVersion("rep")

rt <- robxp(get_robotstxt("https://cdc.gov"))

print(rt)

can_fetch(rt, "/asthma/asthma_stats/default.htm", "*")

can_fetch(rt, "/_borders", "*")

gh_rt <- robxp(robotstxt::get_robotstxt("github.com"))
can_fetch(gh_rt, "/humans.txt", "*") # TRUE
can_fetch(gh_rt, "/login", "*") # FALSE
can_fetch(gh_rt, "/oembed", "CCBot") # FALSE

crawl_delays(gh_rt)

imdb_rt <- robxp(robotstxt::get_robotstxt("imdb.com"))
crawl_delays(imdb_rt)
```

## Test Results

```{r message=FALSE, warning=FALSE, error=FALSE}
library(rep)
library(testthat)

date()

test_dir("tests/")
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.